Multiparty Linear Regression via SPDZ

### 2017-06-15 paper/main.tex
new charts haven't changed words

@@

\begin{figure}[h]
  \includegraphics[width=\linewidth]{results.jpg}
  \caption{(Left) Comparison between different methods of solving linear systems: running time in seconds for Cholesky, LDLT, and CGD (with 5, 10, 15, and 20 iterations) as a function of input dimension. (Middle) Accuracy of CGD as a function of the input on the condition number of the input matrix $A$ with $d = 20$. (Right) Accuracy of Cholesky, LDLT, and CGD, as a function of the input dimensionality $d$. (Top) Fixed-point numbers with the $b = 80$ bits, with 60 in the fractional part. (Bottom) $b = 41$, with 28 in the fractional part}
  \label{fig:result1}
\end{figure}

@@

The run times for SPDZ are always comparable if not much faster. In terms of run-time, we observe that both Cholesky and LDLT were faster for smaller dimensions when $d \leq 100$ and CGD is faster for larger dimensions when $d > 100$. This is consistent with the findings in the original experiment. For dimensions 100 and smaller, when Cholesky and LDLT are faster, they comparative differences are not that big (LDLT with 1.6 seconds compared to CGD 20 with 60.89 seconds) when compared to the largest differences between the larger sizes (LDLT with 1747 seconds and CGD5 with 97 seconds).

@@

>>>>

To better fine tune the CGD and Cholesky algorithms to SPDZ, we ran a few experiments to test hypotheses for

@@

\begin{figure}[h]
  \includegraphics[width=\linewidth]{sqrt.jpg}
  \caption{ (Top) 64 bit (Bottom) 32 bit results }
  \label{fig:result1}
\end{figure}

Comparing square root for Cholesky. In SPDZ, we hypothesized that division would be time consuming, however the behavior does not seem to differ much both in terms of run time and error... Babylonian vs Newton method differ in how many divisions are used in the algorithm. From the results we can see that using different operations don't change the final result. This might be because the way that division is implemented in SPDZ..

For CGD, we decide to test if L2 norm vs Linfinity would make a difference. One utilizes comparisons and the other addition and square root. 
\begin{figure}[h]
  \includegraphics[width=\linewidth]{l2.jpg}
  \caption{ (Top) 64 bit (Bottom) 32 bit results }
  \label{fig:result1}
\end{figure}

Averaged results Averaged column 3 over 30 samples with n = 100000 (avg cn 1.77?)

\vc{compare ranges of error between them???}

N = 100000
\begin{figure}[h]
  \includegraphics[width=\linewidth]{results1.jpg}
  \caption{(Left) Comparison between different methods of solving linear systems: running time in seconds for Cholesky, LDLT, and CGD (with 5, 10, 15, and 20 iterations) as a function of input dimension. (Middle) Accuracy of CGD as a function of the input on the condition number of the input matrix $A$ with $d = 20$. (Right) Accuracy of Cholesky, LDLT, and CGD, as a function of the input dimensionality $d$. (Top) Fixed-point numbers with the $b = 80$ bits, with 60 in the fractional part. (Bottom) $b = 41$, with 28 in the fractional part}
  \label{fig:result2}
\end{figure}

N = 1000
\begin{figure}[h]
  \includegraphics[width=\linewidth]{results2.jpg}
  \caption{(Left) Comparison between different methods of solving linear systems: running time in seconds for Cholesky, LDLT, and CGD (with 5, 10, 15, and 20 iterations) as a function of input dimension. (Middle) Accuracy of CGD as a function of the input on the condition number of the input matrix $A$ with $d = 20$. (Right) Accuracy of Cholesky, LDLT, and CGD, as a function of the input dimensionality $d$. (Top) Fixed-point numbers with the $b = 80$ bits, with 60 in the fractional part. (Bottom) $b = 41$, with 28 in the fractional part}
  \label{fig:result2}
\end{figure}

\vc{talk about outliers in these cases, skews results}

@@

The run times for SPDZ are always comparable if not much faster. In terms of run-time, we observe that both Cholesky and LDLT were faster for smaller dimensions when $d \leq 100$ and CGD is faster for larger dimensions when $d > 100$. This is consistent with the findings in the original experiment. For dimensions 100 and smaller, when Cholesky and LDLT are faster, they comparative differences are not that big (LDLT with 1.6 seconds compared to CGD 20 with 60.89 seconds) when compared to the largest differences between the larger sizes (LDLT with 1747 seconds and CGD5 with 97 seconds). It is also important to note that the time differences between 32 and 64 bits are not that large- only blank percent more compared to the garbled circuits result where doubling the number of bits roughly increased time by an entire magnitude of 10.

Condition number plot
\begin{figure}[h]
  \includegraphics[width=\linewidth]{conditionnumber.jpg}
  \caption{(Left) Comparison between different methods of solving linear systems: running time in seconds for Cholesky, LDLT, and CGD (with 5, 10, 15, and 20 iterations) as a function of input dimension. (Middle) Accuracy of CGD as a function of the input on the condition number of the input matrix $A$ with $d = 20$. (Right) Accuracy of Cholesky, LDLT, and CGD, as a function of the input dimensionality $d$. (Top) Fixed-point numbers with the $b = 80$ bits, with 60 in the fractional part. (Bottom) $b = 41$, with 28 in the fractional part}
  \label{fig:result3}
\end{figure}

@@

- increasing d and increasing the condition number will result in higher errors, so you need more iterations of CGD to get comparable results.
- for high condition numbers, Cholesky outperforms CGD (i.e., gets more accurate results with similar running time).
- for high values of d, but low condition numbers, CGD outperforms Cholesky in both running time and accuracy (that's basically the right column in Figure 6 in the PETS paper)
Regarding the correlation between n, d, and the condition number, increasing d and keeping n constant will result in a higher expected condition number.
(confirmed with Phillipp)
